
\documentclass[]{formatting}
\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     Modified from Deedy Two Column
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\\
% mfsybers@uwaterloo.ca | 289-707-6603 |
%linkedin.com/in/mary-sybersma | github.com/SuberCyber

\namesection{Mary}{Sybersma}{ 2B Computer Science | CAV 86\% }
\sectionsep


\noindent
\begin{minipage}[c]{13cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Classes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Important Classes}
\topline{Current CS Classes}{}
\vskip5pt
\begin{tightemize}
\item Logic and Computation: using \LaTeX to type assignments
\item Object-Oriented Software Development: using Bash and C++ for assignments
\item Computer Organization and Design
\end{tightemize}
\topline{Previous CS Classes}{}
\begin{tightemize}
\item Elementary Algorithm Design and Data Abstraction: used C for assignments
\item Designing Functional Programs: used Scheme (racket) for assignments
\end{tightemize}
%\topline{Other Relevant Classes}{}
%\begin{tightemize}
%\item Linear Algebra II
%\item Calculus III
%\end{tightemize}

\end{minipage} % no space if you would like to put them side by side
\begin{minipage}[c]{0.3\linewidth}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vskip10pt
\section{Skills}
\begin{flushleft} 
\topline{Languages}{}\\
\textcolor{bold} {C}, \space
\textcolor{bold} {C++}, \space
\textcolor{bold} {Bash}, \space
\textcolor{bold} {\LaTeX}, \space
\textcolor{bold} {YAML}, \space
\textcolor{bold} {Scheme}, \space 
\textcolor{bold} {MIPS}, \space
\textcolor{bold} {Javascript}, \space
\textcolor{bold} {HTML}, \space
\textcolor{bold} {CSS} \space\\
\vskip 5pt
\topline{Technologies}{}\\
\textcolor{bold} {Git}, \space
\textcolor{bold} {Jira}, \space
\textcolor{bold} {Concourse}, \space
\textcolor{bold} {Loadrunner}, \space
\textcolor{bold} {TeamCity}, \space
\textcolor{bold} {Fiddler}, \space
\textcolor{bold} {CAD/CAM}, \space
\textcolor{bold} {MongoDB} 
\end{flushleft}
\end{minipage}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work  Experience}

\topline{Ultimate Software, Software Testing Intern} { Sept 2018 - Dec 2018 | Toronto, Ontario}
\begin{tightemize}
\item Analyzed results of Loadrunner tests and provided suggestions for improvements of the services I was testing. 
\item Created build steps to start Loadrunner tests in TeamCity. 
\item Used Loadrunner and C to provide load and stress microservices. 
\item Gathered data for testing purposes using MongoDB and Fiddler.
\item Developed an option for teams to start PSR tests through Concourse using bash and in house tools. 
\end{tightemize}
\sectionsep

\topline{Field Hockey Umpire} {September 2016 – Present | Burlington, ON  \& Waterloo, ON}
\begin{tightemize}
\item Managed games with 22 players on the field with another umpire. 
\item Provided guidance to new players and ensured that the rules of the game were followed. 
\end{tightemize}
\sectionsep

\topline{Wendys's, Cashier and Sandwich Maker}{ September 2014 - April 2017 | Burlington, ON}
\begin{tightemize}
\item Worked in a fast paced environment while ensuring quality of service stayed consistent.  
\item Took initiative to find additional tasks and that my work was done to the best of my ability. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\topline{PSR Testing Option}{Nov 2018 – Dec 2018}
\begin{tightemize}
\item Used Bash and YAML to add a PSR testing option to Concourse pipelines
\end{tightemize}
\sectionsep

\topline{Cribbage Score Counter}{Dec 2018 – Present}
\begin{tightemize}
\item Creating a webpage to calculate best discard option and count score for the card game cribbage using HTML, CSS and Javascript. 
\end{tightemize}
\sectionsep

\topline{Metal Working Projects} {Jan 2014 – June 2017}
\begin{tightemize}
\item Developed a personal pen from blueprint design to fabrication.
\item Designed several small magnets and used a CNC machine and a vertical bandsaw to fabricate them. 
\item Designed and welded a plant stand bicycle. 
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Extracurriculars
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Extracurricular  Activities}

\topline{Math in Europe} {April 2018 – July 2018}
\begin{tightemize}
\item Participated in the Math in Europe study abroad program taking 3 UWaterloo math courses and a french course. 
\item Balanced school work with exploring the cities we stayed in. 
\end{tightemize}
\sectionsep

\topline{Waterloo Math Events} {Jan 2018 – Present}
\begin{tightemize}
\item Educated students in grade 7 to 12 about the Faculty of Mathematics 
\item Presented to groups of 5 to 50 students about Waterloo and lead tours
\end{tightemize}
\sectionsep

\topline {Rotary International} {July 2013 – Aug 2018}
\begin{tightemize}
\item Demonstrated analytic and problem solving skills by analyzing how to best sort garbage correctly and efficiently 
\item  Ability to build strong, influential relationships by staying later ad never turning down an opportunity to help
\end{tightemize}
\sectionsep
 
\end{document}